%------------------------
% Shuvendu Resume
% Author : Shuvendu Dhal
% License : MIT
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\setlength{\footskip}{3.60004pt}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Shuvendu Dhal}} & Email: \href{mailto:}{shuvenduoffline@gmail.com}\\
  \href{https://shuvenduoffline.github.io/}{Portfolio: shuvenduoffline.github.io} & Mobile:~~~+91-8158090295\\
  \href{https://github.com/shuvenduoffline}{Github: ~~github.com/shuvenduoffline} \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{~~Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of calcutta}{Kolkata, India}
      {Bachelor of Technology - Information Technology;  GPA: 8.97}{August 2016 - August 2020}
    %   {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses:} Operating Systems, Data Structures, Analysis Of Algorithms, Artificial Intelligence, Machine Learning, Networking, Databases}}}
         \resumeSubheading
      {J. K. K. I.}{Jharagram, India}
      {Higher Secondary - Science;  Percentage: 83\%}{February 2014 - March 2016}
    %   {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses:} Math, Physics, Chemistry}}}
    \resumeSubHeadingListEnd

%-----------SKILLS-----------------
\vspace{-5pt}
\section{Skills Summary}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{~~~~~~~~JavaScript, JAVA, C++}
	\resumeSubItem{Frameworks}{~~~~~~NodeJS, React, Spring Boot}
	\resumeSubItem{Tools}{~~~~~~~~~~~~~~~~Nginx, Kafka, MongoDb, MySQL}
	\resumeSubItem{Platforms}{~~~~~~~~~Linux, Web, Windows, AWS}
	\resumeSubItem{Soft Skills}{~~~~~~~~~Leadership, Blogging}

\resumeSubHeadingListEnd
\vspace{-5pt}
%-----------Experience-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading{Passionate Solver Technologies}{Kolkata, India}
    {Software Engineer (Full-time)}{Sept 2021 - Present}
    \resumeItemListStart
        \resumeItem{Aggregator for IOT-Water }
          {Build micro-service to aggregate IOT water data. }
          \resumeItem{REST API for IOT-Dashboard}
          {IOT data processed and converted to API interface.}
          \resumeItem{Server Provision and Migration}{AWS EC-2 provisioning, deployment of services, and migration.}
          \resumeItem{Impact}{Reduction of water and energy wastage by 30\% on average.}
          \resumeItem{Link}{\href{https://waterdist.iot.demo.passionatesolver.com/login}{waterdist.iot.demo.passionatesolver.com}}
      \resumeItemListEnd
      
    \resumeSubheading{Austec Service Pty Ltd}{Rocklea QLD, Australia}
    {Software Engineer Freelance (Part-time,Remote)}{May 2020 - Nov 2020}
    \resumeItemListStart
        \resumeItem{Guard Shift Assignment}
          {Build a web app to assign shifts to security guards.}
          \resumeItem{Shift Monitoring}
          {Developed mobile application to track guards shift based on location and time.}
          \resumeItem{Team Lead}{Lead the team of 3 interns, successfully deliver in time.}
          \resumeItem{Impact}{Simplified the workings of 1000+ security guards and reduced the day-to-day scheduling efforts by 3x.}
          \resumeItem{Link}{\href{http://www.employee.austecservices.com.au}{employee.austecservices.com.au}}
      \resumeItemListEnd  
      
% \vspace{-1pt}
    \resumeSubheading
		{Xoriant Solutions Pvt ltd}{Pune, India}
		{Associate Software Engineer (Full-time)}{Nov 2020 -  Sept 2021}
		\resumeItemListStart
        \resumeItem{Disk Clean Service}
          {Created micro-service to clean up old files based on schedule and file status.}
        \resumeItem{Service Discovery}
          {Enabled service discovery with Netflix Eureka to add/remove micro-services dynamically. }
        \resumeItem{Impact}{Improved server performance and up time of services significantly. }
		\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\vspace{-5pt}
\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{Open Source Contribution - p2p-deploy}{Build and published npm package for running ci/cd command in a
secure away from the client machine to the server. The output of
the commands is shown on the client-side in real-time. Build with nodes inbuild features without any other dependency.}
\vspace{5pt}
\newline{}
\textbf{Link : }{\href{https://www.npmjs.com/package/p2p-deploy}{npmjs.com/package/p2p-deploy}}

\resumeSubItem{Reservation and food booking with WhatsApp Chat Bot}{Build on twilio, integrated with reservation platform using cloud functions. The cafe could book and manage booking through an interactive dashboard. Boosted revenue by 30\%.}
\vspace{5pt}
\newline{}
\textbf{Tech : }{Twilio, NodeJS, Cloud Function, Firebase, React}

\resumeSubItem{Web3 Blood Bank}{The new generation's blood bank, powered by the Ethereum blockchain build with solidity. Blood bottles can be tracked from their origin to the end-user with block chains power and its security keeping all data safe and immutable.}
\vspace{5pt}
\newline{}
\textbf{Tech : }{Solidity, React}
\newline{}
\textbf{Link :}{\href{https://shuvenduoffline.github.io/bloodbank/#/}{shuvenduoffline.github.io/bloodbank/}}

% --------------- PUBLICATION ------------------------

\section{Publications}
\resumeSubHeadingListStart
\resumeSubItem{Paper: Web3 Decentralize Application}{(Work in Progress) Blockchain based framework for document sharing, preserving and verification using ethereum blockchain.}
\resumeSubHeadingListEnd
\vspace{-5pt}
%-----------Awards-----------------
\section{Honors and Awards}
\begin{description}[font=$\bullet$]
\item {Runner's Up at Airbus Aerothon, Lead a team of 4 to build the solution in 7days - July, 2022}
\vspace{-5pt}
\item {Copyright in Web3 dApp solution - January, 2021 }



\end{description}

% \vspace{-5pt}
% \section{Volunteer Experience}
%   \resumeSubHeadingListStart
% 	\resumeSubheading
%     {Community Lead at Developer Student Clubs NSEC}{Kolkata, India}
%     {Conducted online and offline technical \& soft-skills training impacting over 3000 students.}{Jan 2019 - Present}
% \vspace{5pt}
%     % \vspace{10pt}\textbf{\large{Community Experience}}
%     \resumeSubheading
%     {Event Organizer at Google Developers Group Kolkata}{Kolkata, India}
%     {Organized events, conducted workshops and delivered workshops reaching over 7000 developers.}{Jan 2018 - Present}

\resumeSubHeadingListEnd

\end{document}
